Comparing vector-based and ACT-R memory models of tag retrieval:\protect\\User-customized hashtag/tag prediction on Twitter and StackOverflow

### 2013-11-05 writeups/proposal/proposal.tex
foo
Former-commit-id: 6dd3aef4bf858f8aa203d221a32a175cce575071 [formerly be7e18366dbc8d2350cfdd87fb1eb65ae616d993]
Former-commit-id: 8d00c6a2f5d99e965343f471fff62e29a16f25d9

One method to include word order in a Bayesian co-occurrence matrix is to represent word position on a third, orthogonal dimension, and turn the matrix into a 3-dimensional array.
So a co-occurrence is represented by a triplet: context word by word position relative to tag by tag.
When a retrieval request for a tag is made, the strength of association between each word in context (and its position) and the tags in the co-occurrence array would be computed.
That computation could be made tractable by storing only a small set of orders on the dimension axis and binning.

For example, one could store only three: near, medium, far, which is equivalent to storing three separate co-occurrence matrices.
So when a retrieval request is made (e.g., when a user writes the \# character when composing a tweet), the strength of association for each word would be computed using the appropriate matrix.
That is, the ``far'' matrix would be used for words far away from the cursor position, ``near'' for words just written, and ``medium'' for words mid distance from the current focus point.
This method seems straightforward to implement, but it is slightly unsatisfying since information is lost when binning is used.
So I will try to discover a better technique to incorporate word order information into the ACT-R Bayesian model than the one just described, but will fall back to this technique if a better method is not found.

>>>>

One method to include word order in a Bayesian co-occurrence matrix is to represent word position on a third, orthogonal dimension, and turn the matrix into a 3-dimensional array.
So a co-occurrence is represented by a triplet: context word by word position relative to tag by tag.
When a retrieval request for a tag is made, the strength of association between each word in context (and its position) and the tags in the co-occurrence array would be computed.
That computation could be made tractable by storing only a small set of values on the order axis and binning.

For example, one could store only three: near, medium, far, which is equivalent to storing three separate co-occurrence matrices.
So when a retrieval request is made (e.g., when a user writes the \# character when composing a tweet), the strength of association for each word would be computed using the appropriate matrix.
That is, the ``far'' matrix would be used for words far away from the cursor position, ``near'' for words just written, and ``medium'' for words mid distance from the current focus point.
This method seems straightforward to implement, but it is slightly unsatisfying since information is lost when binning is used.
It also does not scale, since an additional 2-dimensional sparse matrix must be added for every additional value stored on the word order dimension.
So I will try to discover a better technique to incorporate word order information into the ACT-R Bayesian model than the one just described, but will fall back to this technique if a better method is not found.
